Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-06 ms.tex
spelling

In the presence of strong heating, one-dimensional steady-state flow
is characterized by an inflow-outflow structure, with a critical
radius known as the``stagnation radius" $\rs$ where the radial
velocity passes through zero.  Mass loss from stars interior to the
stagnation radius is accreted, while that outside $\rs$ is unbound in
an outflow from the nucleus.  The stagnation radius, rather than the
Bondi radius, thus controls the SMBH accretion rate (although we will
show that $\rs$ will in many cases reside near the nominal Bondi
radius).  When heating is sufficiently weak, however, the stagnation
radius may move to much larger radii or not exist at all, in which case the entire ISM of the galaxy is flowing
towards the SMBH.  A goal of this work is to assess under what
conditions a stagnation radius exists, as this question is intimately
tied to that of cooling instability.
% Furthermore, in some cases we find that no stagnation
% radius exists at all; this formally implies that the entire of ISM of
% the galaxy is feeding the SMBH, potentially resulting in much higher
% accretion rate than would be predicted by simple Bondi accretion.

>>>>

In the presence of strong heating, one-dimensional steady-state flow
is characterized by an inflow-outflow structure, with a critical
radius known as the``stagnation radius" $\rs$ where the radial
velocity passes through zero.  Mass loss from stars interior to the
stagnation radius is accreted, while that outside $\rs$ is unbound in
an outflow from the nucleus.  The stagnation radius, rather than the
Bondi radius, thus controls the SMBH accretion rate (although we will
show that $\rs$ will in many cases resides near the nominal Bondi
radius).  When heating is sufficiently weak, however, the stagnation
radius may move to much larger radii or not exist at all, in which case the entire ISM of the galaxy is flowing
towards the SMBH.  A goal of this work is to assess under what
conditions a stagnation radius exists, as this question is intimately
tied to that of cooling instability.
% Furthermore, in some cases we find that no stagnation
% radius exists at all; this formally implies that the entire of ISM of
% the galaxy is feeding the SMBH, potentially resulting in much higher
% accretion rate than would be predicted by simple Bondi accretion.
